### 2020-09-07 tex/results.tex
first commit

\vspace{-0.2cm}

@@

\begin{table}[!t]
\centering
\caption{FPGA resource consumption of the proposed FrodoKEM \textbf{KeyGen} designs, using $k$ parallel multipliers, for both parameter sets, on a Xilinx Artix-7 FPGA.}\label{tab:keyresults}
%\vspace{-.2cm}
%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
\begin{tabular}{l r r r c c r}
\hline \Tstrut
  \textsc{FrodoKEM} & \multirow{2}{*}{LUT} & \multirow{2}{*}{FF} & \multirow{2}{*}{Slices} & DSP/ & \multirow{2}{*}{MHz} & Ops/ \\
Protocol &&&& BRAM && Sec  \\ \hline \Tstrut
%\textbf{} & & & \textbf{BRAM} & &\textbf{Sec} \\ \hline

@@

\end{tabular}%}
\end{table}

\begin{table}[!t]
\centering
\caption{FPGA resource consumption of the proposed FrodoKEM \textbf{Encapsulation} designs, using $k$ parallel multipliers, for both parameter sets, on a Xilinx Artix-7 FPGA.}\label{tab:encapsresults}
%\vspace{-.2cm}
%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
\begin{tabular}{l r r r c c r}
\hline \Tstrut
  \textsc{FrodoKEM} & \multirow{2}{*}{LUT} & \multirow{2}{*}{FF} & \multirow{2}{*}{Slices} & DSP/ & \multirow{2}{*}{MHz} & Ops/ \\
Protocol &&&& BRAM && Sec  \\ \hline \Tstrut
%\textbf{} & & & \textbf{BRAM} & &\textbf{Sec} \\ \hline

@@

\end{tabular}%}
\end{table}

@@

There is a significant increase in area consumption of all the decapsulation results which do not utilize BRAM. This is mainly due to the need of storing public-key and secret-key matrices. We provide results for both architectures with and without BRAM. The design without BRAM has a significantly higher throughput, due to the much higher frequency. %These results are reported in Figure \ref{fig:hw_line}, which shows the efficiency of each design (namely their throughput) per FPGA slice utilized. 
Figure \ref{fig:hw} shows a slice count summary of all the proposed designs, showing a consistent and fairly linear increase in slice utilization as the number of parallel multipliers increases. We note on decapsulation results in Figure \ref{fig:hw} where the results would lie if BRAM is used, hence the total results for without BRAM include both red areas (i.e., they overlap). In most cases slice counts at least double for decapsulation when BRAM is removed, with only slight increases in throughout, hence it might be not be useful in some use cases. BRAM usage, however, is not as friendly when hardware designs are considered for ASIC, thus is it useful to consider designs both with and without BRAM.

\begin{table}[!t]
\centering
\caption{FPGA resource consumption of the proposed FrodoKEM \textbf{Decapsulation} designs, using $k$ parallel multipliers, for both parameter sets, on a Xilinx Artix-7 FPGA. *BRAM used}\label{tab:decapsresults}
%\vspace{-.2cm}
%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
\begin{tabular}{l r r r c c r}
\hline \Tstrut
  \textsc{FrodoKEM} & \multirow{2}{*}{LUT} & \multirow{2}{*}{FF} & \multirow{2}{*}{Slices} & DSP/ & \multirow{2}{*}{MHz} & Ops/ \\
Protocol &&&& BRAM && Sec  \\ \hline \Tstrut
%\textbf{} & & & \textbf{BRAM} & &\textbf{Sec} \\ \hline

@@

\end{tabular}%}
\end{table}

\begin{table}[!t]
\centering
\caption{FPGA resource consumption of the proposed PRNG and Error Sampler designs on a Xilinx Artix-7 FPGA.}\label{tab:otherresults}
%\vspace{-.2cm}
%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
\begin{tabular}{l r r r c c r}
\hline \Tstrut
  \textsc{FrodoKEM} & \multirow{2}{*}{LUT} & \multirow{2}{*}{FF} & \multirow{2}{*}{Slices} & DSP/ & \multirow{2}{*}{MHz} & Ops/ \\
Protocol &&&& BRAM && Sec  \\ \hline \Tstrut
%\textbf{} & & & \textbf{BRAM} & &\textbf{Sec} \\ \hline

@@

\end{tabular}%}
\end{table}

\begin{figure}[h]
\centering
%    \advance\leftskip-1cm
\resizebox{0.4\textwidth}{!}{%
\input{figures/hw.tikz}
}
\caption{Visualisation of FPGA slice consumption of FrodoKEM's key generation, encaps, and decaps on a Xilinx Artix-7. Decaps values overlap to show results with (*) and without BRAM.}
\label{fig:hw}
\end{figure}

@@

%\begin{figure}[h]
%\centering
%    \advance\leftskip-1cm
%\resizebox{0.45\textwidth}{!}{%
%\input{figures/hw_line.tikz}}
%\caption{Comparison of the throughput performance per FPGA slice on a Xilinx Artix-7.}
% \label{fig:hw_line}
%\end{figure}

>>>>

@@

\begin{table}
\centering
\caption{FPGA resource consumption of the proposed FrodoKEM \textbf{KeyGen} designs, using $k$ parallel multipliers, for both parameter sets, on a Xilinx Artix-7 FPGA.}\label{tab:keyresults}
%\vspace{-.2cm}
\resizebox{\columnwidth}{!}{

%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
\begin{tabular}{l r r r c c r}
\hline \Tstrut
  \textsc{FrodoKEM} & \multirow{2}{*}{LUT} & \multirow{2}{*}{FF} & \multirow{2}{*}{Slices} & DSP/ & \multirow{2}{*}{MHz} & Ops/ \\
Protocol &&&& BRAM && Sec  \\ \hline \Tstrut
%\textbf{} & & & \textbf{BRAM} & &\textbf{Sec} \\ \hline

@@

\end{tabular}}
\end{table}

\begin{table}
\centering
\caption{FPGA resource consumption of the proposed FrodoKEM \textbf{Encapsulation} designs, using $k$ parallel multipliers, for both parameter sets, on a Xilinx Artix-7 FPGA.}\label{tab:encapsresults}
%\vspace{-.2cm}
%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
\resizebox{\columnwidth}{!}{

\begin{tabular}{l r r r c c r}
\hline \Tstrut
  \textsc{FrodoKEM} & \multirow{2}{*}{LUT} & \multirow{2}{*}{FF} & \multirow{2}{*}{Slices} & DSP/ & \multirow{2}{*}{MHz} & Ops/ \\
Protocol &&&& BRAM && Sec  \\ \hline \Tstrut
%\textbf{} & & & \textbf{BRAM} & &\textbf{Sec} \\ \hline

@@

\end{tabular}}
\end{table}

@@

There is a significant increase in area consumption of all the decapsulation results which do not utilize BRAM. This is mainly due to the need of storing public-key and secret-key matrices. We provide results for both architectures with and without BRAM. The design without BRAM has a significantly higher throughput, due to the much higher frequency. These results are reported in Figure \ref{fig:hw_line}, which shows the efficiency of each design (namely their throughput) per FPGA slice utilized. 
Figure \ref{fig:hw} shows a slice count summary of all the proposed designs, showing a consistent and fairly linear increase in slice utilization as the number of parallel multipliers increases. We note on decapsulation results in Figure \ref{fig:hw} where the results would lie if BRAM is used, hence the total results for without BRAM include both red areas (i.e., they overlap). In most cases slice counts at least double for decapsulation when BRAM is removed, with only slight increases in throughout, hence it might be not be useful in some use cases. BRAM usage, however, is not as friendly when hardware designs are considered for ASIC, thus is it useful to consider designs both with and without BRAM.

\begin{table}
\centering
\caption{FPGA resource consumption of the proposed FrodoKEM \textbf{Decapsulation} designs, using $k$ parallel multipliers, for both parameter sets, on a Xilinx Artix-7 FPGA. Asterisk (*) denotes designs that used BRAM.}\label{tab:decapsresults}
%\vspace{-.2cm}
%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
\resizebox{\columnwidth}{!}{

\begin{tabular}{l r r r c c r}
\hline \Tstrut
  \textsc{FrodoKEM} & \multirow{2}{*}{LUT} & \multirow{2}{*}{FF} & \multirow{2}{*}{Slices} & DSP/ & \multirow{2}{*}{MHz} & Ops/ \\
Protocol &&&& BRAM && Sec  \\ \hline \Tstrut
%\textbf{} & & & \textbf{BRAM} & &\textbf{Sec} \\ \hline

@@

\end{tabular}}
\end{table}

\begin{table}
\centering
\caption{FPGA resource consumption of the proposed PRNG and Error Sampler designs on a Xilinx Artix-7 FPGA.}\label{tab:otherresults}
%\vspace{-.2cm}
%\resizebox{0.7\textwidth}{!}{
%\noindent\makebox[\textwidth]{
\resizebox{\columnwidth}{!}{

\begin{tabular}{l r r r c c r}
\hline \Tstrut
  \textsc{FrodoKEM} & \multirow{2}{*}{LUT} & \multirow{2}{*}{FF} & \multirow{2}{*}{Slices} & DSP/ & \multirow{2}{*}{MHz} & Ops/ \\
Protocol &&&& BRAM && Sec  \\ \hline \Tstrut
%\textbf{} & & & \textbf{BRAM} & &\textbf{Sec} \\ \hline

@@

\end{tabular}}
\end{table}

\begin{figure}
\centering
%    \advance\leftskip-1cm
%\resizebox{0.4\textwidth}{!}{%
\resizebox{\columnwidth}{!}{

\input{figures/hw.tikz}
}
\caption{Visualisation of FPGA slice consumption of FrodoKEM's key generation, encaps, and decaps on a Xilinx Artix-7. Decaps values overlap to show results with (*) and without BRAM.}
\label{fig:hw}
\end{figure}

@@

\begin{figure}
\centering
    \advance\leftskip-1cm
%\resizebox{0.45\textwidth}{!}{%
\resizebox{\columnwidth}{!}{
\input{figures/hw_line.tikz}}
\caption{Comparison of the throughput performance per FPGA slice on a Xilinx Artix-7.}
 \label{fig:hw_line}
\end{figure}
